% ************************** Thesis Acknowledgements *****************************
\begin{acknowledgements}
%% Thanks Supervisor DONE
I would like to first thank my supervisor, Prof. Dr. Katsuaki Koike, for all of his support, encouragement, and advice over the years. Koike-sensei's precious and steady support allowed me to grow into a contributing member of the scientific community.
He gave me substantial liberties, but was always been available to aid in my understanding of problems and to give ideas when I was unsure of what to do going forward. I could not have completed this work without him.
%% Thanks Vice Supervisors DONE
I also would like thank my vice supervisors, Asso. Prof. Dr. Yoshitada Mito and Asso. Prof. Dr. Yosuke Higo. Especially I am grateful to Mito-sensei as my asvisor of “The Education Program for Global Leaders in Advanced Engineering and Pharmaceutical Sciences (GL), Kyoto University”.
%% Thanks Committee  WAIT
My grateful thanks also extend to my committee members as well.  Prof. Dr. Tamura  and Prof. Dr. Mito have reviewed my dissertation and offered valuable insight. My work has been better for their input.
%% Thanks Lab TODO
I would like to thank all staffs and members in the "Laboratory of Geosphere Environment, Kyoto Univerity" and  "Laboratory of Applied Geosciences and Technology, Kumamoto University". GL member, GELK members, especiaaly KASHIWAYA, Kouki, and Asaue for their many valuable discussions

%% Thanks Scholarship and Support TODO
I am really appreciate to scholarships and projects fund which supported me in my study.  Without the supports  from them, this research would not have been completed.  unit in the brace is Japanese yen. 
1. 1,000, 000
2.  
3.
4.
5.
6.

7.
Especially GL project supported me have  a
four month internship in Asia Disaster Reduction Center(ADRC ) , Kobe. 
after that ADRC provided me a GIS and Remote sensing lecture position of training visitor researchers. This position not only support me financially but also give me chance to communicate with yong scientist from Asia countries. I need to  thank all the members and research visitors from ADRC, especially thanks to natori Sugiura  shiomi  and ikeda san. for their help and advice in sentinel Asia project. 
Also, I  have to thanks all  the members of  geologocal  remote sensing group  of AIST especially→ urai  who provided the one month internship in the institute of Japan geology. 





Steve Saleeby, thank you for the budgeting code, and for countless modeling questions answered.  Tristan L'Ecuyer, thank you for your help and insight into observational data, and for your helpful suggestions as a co-author.  Matt Lebsock, thank you for providing model data, and for helpful conversations about dealing with satellite data.  Natalie Tourville, thank you for keeping my computers working over the past few years.  All of the members of the van den Heever research group have been a great help, and I think them all for the useful conversations and the fun ones.  I need to express my gratitude to my friends and family who have supported me through this process, and haven't let a crazy, stressed out grad student scare them away.

%% Thanks family DONE
Finally, I would like to dedicate this dissertation to my beloved wife Ling Wang, and my parents, sisters and brother. Without their patient love, encouragement and constant support, this research could not have been completed. Especially, I would like to give my special thanks to my wife Ling who has always worked to make my life happy and fulfilling with love.
\end{acknowledgements}
